---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# firesafety

<!-- badges: start -->
[![R-CMD-check](https://github.com/thomasp85/firesafety/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/thomasp85/firesafety/actions/workflows/R-CMD-check.yaml)
[![Codecov test coverage](https://codecov.io/gh/thomasp85/firesafety/graph/badge.svg)](https://app.codecov.io/gh/thomasp85/firesafety)
<!-- badges: end -->

This package contains a collections of plugins for [fiery](https://fiery.data-imaginist.com) that handles server-side security in different ways. Currently it contains:

### `SecurityHeaders`
Inspired by [helmet.js](https://helmetjs.github.io), this plugin will configure and set a range of security related headers on all outgoing responses.

### `CORS`
This plugin will help you set up Cross-Origin-Resource-Sharing (CORS) for one or more paths in your server.

### `ResourceIsolation`
This plugin lets you configure Resource Isolation Policies for one or more paths in your server.

## Installation

``` r
# You can install marquee from CRAN
pak::pak("firesafety")

# Or get the development version from Github
pak::pak("thomasp85/firesafety")
```

## Examples
Using the plugins is straightforward as they all come with sensible defaults that serve as a good starting point. Remember the best security is _as strict as your functionality allows_. If you find that your server logic no longer works after adding these any of these plugins, investigate why, and relax the settings for the specific area that is causing issues.

```{r}
app <- fiery::Fire$new()

# Set security headers but remove those related to UI (we assume this is a REST
# server) and rely on defaults for the rest
headers <- firesafety::SecurityHeaders$new(
  content_security_policy = NULL,
  cross_origin_embedder_policy = NULL,
  cross_origin_opener_policy = NULL,
  origin_agent_cluster = NULL,
  referrer_policy = NULL,
  x_dns_prefetch_control = NULL,
  x_download_options = NULL,
  x_frame_options = NULL,
  x_xss_protection = NULL
)

# decrease the max age of STS after creation
headers$strict_transport_security <- firesafety::sts(
  max_age = 31536000 # 1 year
)

# Add to server
app$attach(headers)

# Set up CORS for a subset of paths
cors <- firesafety::CORS$new(
  path = "global/*",
  origin = "https://my-other-website.com"
)

# Add to server
app$attach(cors)

# Set up RIP for a path and its subpaths
rip <- firesafety::ResourceIsolation$new(
  path = "assets/*",
  allowed_site = "same-origin"
)

# Add to server
app$attach(rip)

app
```
